Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-31 outputs/paper/paper.qmd
trying to visualize number of subdivisions by ward

## Load packages
library(tidyverse)
library(knitr)
library(here)
library(sf)
library(ggplot2)
library(ggspatial)

@@

>>>>

## Load packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)
library(sf)
library(ggplot2)
library(ggspatial)
library(lubridate)

@@

# summarize ward data by number of subdivisions

head (cleaned_voter_statistics, 5) |>
 select(ward, sub, percent_voted) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub", "Percent Voted"),
  booktabs = TRUE
  )

cleaned_voter_statistics |>
  slice(2:53)

  filter("ward" == 1) |>
  select(ward, sub)
